Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-04-26 tese/section01.tex
more on webrtc

>>>>

\ac{WebRTC} defines three main \ac{API}s: GetUserMedia, PeerConnection and DataChannel.

\begin{itemize}
  \item \textbf{GetUserMedia} allows from the browser to access to camera, microphone and device screen.

  \item \textbf{PeerConnection} aquires connection data and negotiates with peers.

  \item \textbf{DataChannel} allows to send whatever type of data to other peers.
\end{itemize}

### 2015-04-26 tese/section03.tex
more on webrtc

{\color{red} [svg is more than this]}

  Video functionalities are already embedded in \ac{HTML}5, like \ac{SVG} it is also possible to bind javascript functions for different kinds of events over videos.

>>>>

  Video and audio functionalities are already possible with \ac{HTML}5, like \ac{SVG} it is also possible to bind javascript functions for different kinds of events over video and audio elements.
